Tables for PM2.5 Components Paper Manuscript

### 2021-06-06 code/data-viz/manuscript-tables.Rmd
main text tables

```{r Load data}
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

>>>>

```{r Load data}
load(here('data','processed', 'pmc-daily.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))

load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

### Table 2
```{r}
dt.pmc <- dt.pmc.site.ndi %>% 
  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
         Region = ifelse(Region.IV == 1, "West",
                         ifelse(Region.IV == 2, "Midwest",
                                ifelse(Region.IV == 3, "South", "Northeast"))),
         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast"))) %>%
  select(Site.ID, Region, Loc.Set) %>% 
  merge(dt.pmc.daily) %>% 
  pivot_longer(AS:PM,
               names_to = "Parameter",
               values_to = "Value")

table.region <- dt.pmc %>% 
  group_by(Parameter, Region) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000)))

table.urban <- dt.pmc %>% 
  group_by(Parameter, Loc.Set) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
  mutate(Region = Loc.Set,
         Region = factor(Region, levels = c("Urban", "Rural"))) %>% 
  select(-Loc.Set) %>% 
  arrange(Region)

cmp <- c("PM", "AS", "CA", "CL", "CU", "FE", "K", "MG", "MN", "NA", "NI",
         "NO3", "OC", "PB", "SE", "SI", "SO4", "V", "ZN")

table <- dt.pmc %>% 
  group_by(Parameter) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
  mutate(Region = "US",
         Region = factor(Region, levels = c("US"))) %>% 
  as.data.frame() %>% 
  add_row(table.region) %>% 
  add_row(table.urban) %>% 
  filter(Parameter != "EC") %>% 
  mutate(test = paste(Mean,"±",STD, sep = " ")) %>% 
  select(-Mean, -STD) %>% 
  pivot_wider(names_from = "Region",
              values_from = "test",
              names_sort = F) %>% 
  mutate(Parameter = factor(Parameter, levels = cmp)) %>% 
  arrange(Parameter) %>% 
  rename(Component = Parameter)

ft <- flextable(table)
ft <- theme_booktabs(ft)
ft <- vline(ft, j = c('Component', 'US', 'Northeast'))
ft <- hline(ft, i = c(1, 4, 7, 10, 13, 16))
ft <- padding(ft, padding = 0)
ft <- fontsize(ft, size = 10)
ft <- set_caption(ft, caption = "Table 2. Daily concentrations of PM2.5 and its components, mean ± standard deviation, nationwide, by region and urbanicity.")
ft <- fontsize(ft, i = 1, size = 12, part = "header")
ft <- autofit(ft)

doc <- read_docx()
doc <- body_add_flextable(doc, value = ft, split = T)
doc <- body_add_par(doc, "Units are ng/m3 unless specified", style = "Normal")
body_add(doc, run_pagebreak())
```

### Table 3
```{r}
fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
factor.loadings <- rbind(fit$loadings) %>% as.data.frame()
factor.loadings <- rownames_to_column(factor.loadings, "Component")

colnames(factor.loadings) <- c("Component", "Soil", "Metals", "Traffic", 
                               "Biomass Combustion", "Coal combustion", "Salt", 
                               "Residual Oil Combustion", "Steel Industry") 
factor.loadings <- factor.loadings %>% 
  mutate_at(.vars = c("Soil", "Metals", "Traffic", "Biomass Combustion", 
                      "Coal combustion", "Salt", "Residual Oil Combustion", 
                      "Steel Industry"), ~sprintf('%.2f', .x))

ft <- flextable(factor.loadings)
ft <- theme_booktabs(ft)
ft <- vline(ft, j = c('Component'))
ft <- hline(ft, i = c(3, 6, 9, 12, 15))
ft <- padding(ft, padding = 0)
ft <- fontsize(ft, size = 10)
ft <- set_caption(ft, caption = "Table 3. Loadings of each component for eight identified factors.")
ft <- fontsize(ft, i = 1, size = 12, part = "header")
ft <- autofit(ft)

doc <- body_add_flextable(doc, value = ft, split = T)
body_add(doc, run_pagebreak())

print(doc, target = here('output','table','main-tables.docx'))
```
